%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Mohaymen} % Organization
    {Tehran, Iran} % Location
    {May. 2016 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on BI project. Showing charts from some data in our database.}
        \item {We used ASP.NET MVC for our back-end framework and JQuery as our front-end library.}
        \item {Used SQL Server, Entity Framework, Highcharts, JQuery UI, Gridster, Razor, Kendo UI Library, Azure Devops, Confluence}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Full Stack Developer} % Job title
{Mohaymen} % Organization
{Tehran, Iran} % Location
{May. 2017 - Aug. 2021} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Working on LA (Link Analysis) project.}
	\item {Work on LA project from scratch.}
	\item {Participating in refining user stories.}
	\item {Start with unit testing in front-end and back-end developments.}
	\item {Used SQL Server, SQLite, Entity Framework, SignalR, Kendo UI Library, Karma, XUnit, Ogma (for graph visualization), Mapbox GL (for map visualization), Azure Devops, Jira, Confluence}
\end{cvitems}
}

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Team Lead} % Job title
    {Mohaymen} % Organization
    {Tehran, Iran} % Location
    {Sep. 2021 - Aug. 2022} % Date(s)
    {
    	\begin{cvitems} % Description(s) of tasks/responsibilities
    		\item {Working on LA (Link Analysis) project as team lead.}
    		\item {Participating in refining backlogs and tasks.}
    		\item {Participating in on-boarding process of new staff.}
    		\item {Managing and scheduling tasks with team members using planning poker.}
    		\item {Scheduling training sessions to reach the maximum potential of team members.}
    		\item {Reviewing PRs of team members.}
    		\item {Pair programming with other team members.}
    		\item {Used SQL Server, SQLite, Entity Framework, SignalR, WebSocket, TileServerGL (for our map tiles server), Graph Hopper (for search over map) , Kendo UI Library, Ogma (for graph visualization), Karma, XUnit, NGZorro, Mapbox GL (for map visualization), Azure Devops, Jira, Confluence}
    	\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front End Engineer} % Job title
    {Sarmad Insurance} % Organization
    {Tehran, Iran} % Location
    {Sep. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Working for 3 web applications in Sarmad Insurance Company.}
      	\item {These 3 portals consist of admin portal, users portal and main website.}
        \item {Design and implement new features.}
        \item {Maintain developed components.}
        \item {Used NGZorro, PrimeNG, GraphQL, PWA, Jest, NX Monorepo, Mapbox GL (for map visualization), Gitlab, Trello}
      \end{cvitems}
    }

%---------------------------------------------------------


%---------------------------------------------------------
\cventry
{Front End Engineer} % Job title
{Jiring} % Organization
{Tehran, Iran} % Location
{Dec. 2022 - Present} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Working on a SMS Bulk Application from scratch.}
		\item {Design and implement new features.}
		\item {Used NGZorro, Cytoscape (for graph visualization), Gitlab, Jira}
	\end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
