%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Freelancer} % Affiliation/role
    {Anahid Travel Agency} % Organization/group
    {Iran} % Location
    {Nov. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designing and implementing the website for this agency.}
        \item {Working on that as full-stack developer.}
        \item {There are two panels in this website. Admin panel and the main website for client usage.}
        \item {During this project I've worked with the following framework, tools and libraries:  C\#, .NET Core, Entity Framework, SQL, Angular, Typescript, Angular Material, Highcharts.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelancer} % Affiliation/role
    {Arad} % Organization/group
    {Iran} % Location
    {Jan. 2022 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {This website is for project management.}
        \item {Working on that as a front-end developer.}
        \item {It has some panels to create project and assign some users to those projects.}
        \item {During this project I've worked with the following framework, tools and libraries:  Angular, Typescript, Angular Material, Highcharts.}
      \end{cvitems}
    }

%---------------------------------------------------------
	\cventry
	{Freelancer} % Affiliation/role
	{IbimVillage} % Organization/group
	{Iran} % Location
	{Jun. 2022 - Aug. 2022} % Date(s)
	{
		\begin{cvitems} % Description(s) of experience/contributions/knowledge
			\item {This website is for BIM model designing.}
			\item {Working on that as a front-end developer.}
			\item {It has some panels to create project and assign some users to those projects to some BIM model designers.}
			\item {During this project I've worked with the following framework, tools and libraries: : Angular, Typescript, Angular Material, Highcharts, MapboxGL.}
		\end{cvitems}
	}

%---------------------------------------------------------
\end{cventries}
